---
title: "Data Preparation"
output:
  html_document:
    toc: TRUE
    toc_float:
      collapsed: FALSE
    toc_depth: 2
    code_folding: show
    df_print: paged
bibliography      : 
  - "bibliography/r-references.bib"
  - "bibliography/references.bib"
---

```{r knitr-setup, include=F}
set.seed(170819)

knitr::opts_chunk$set(
  warning=F, 
  echo=T, 
  error=F, 
  message=F, 
  cache = T, 
  tidy=T, 
  dev = 'pdf', 
  cache.extra = knitr::rand_seed,
  fig.height = 6,
  fig.width = 8
  )

options(
  digits = 3, 
  width = 150,
  max.print = 100000000
  )
```

Here we outline how we prepared the data for our analyses, including quality checks.

# Data

Please first download the data from [AUSSDA](https://data.aussda.at/dataset.xhtml?persistentId=doi:10.11587/IC66GC) and put it into the folder "data".

# Set-up

We load the packages.

```{r r-setup, include=T, echo=T, results='hide', cache=F}
# install packages
# devtools::install_github("https://github.com/tdienlin/td")

library(confintr)
library(corrplot)
library(easystats)
library(ggplot2)
library(kableExtra)
library(knitr)
library(lavaan)
library(magrittr)
library(MVN)
library(naniar)
library(PerFit)
library(psych)
library(sjlabelled)
library(semTools)
library(tidyverse)
library(td)

load("data/workspace_1.RData")
source("custom_functions.R")
```

We next load the data.

```{r data-wrangling}
d_raw <- sjlabelled::read_spss(
  "data/10849_da_en_v1_0.zsav",
  convert.factors = FALSE
  )
```

# Data Preparation

## Recoding

We need to recode inverted items, rename variables, and recode variables (Age was coded wrongly).

```{r data-inverting}
vars_invert <- c(
  "HEX_HOH_SIN_01", "HEX_HOH_SIN_03",
  "HEX_HOH_FAI_01", "HEX_HOH_FAI_02", "HEX_HOH_FAI_04",
  "HEX_HOH_GRE_02", "HEX_HOH_GRE_03", "HEX_HOH_GRE_04",
  "HEX_HOH_MOD_03", "HEX_HOH_MOD_04",
  "HEX_EMO_FEA_02", "HEX_EMO_FEA_04",
  "HEX_EMO_ANX_02", "HEX_EMO_ANX_03",
  "HEX_EMO_DEP_02", "HEX_EMO_DEP_04",
  "HEX_EMO_SEN_04",
  "HEX_EXT_SSE_03", "HEX_EXT_SSE_04",
  "HEX_EXT_BOL_01", "HEX_EXT_BOL_04",
  "HEX_EXT_SOC_01",
  "HEX_EXT_LIV_03", "HEX_EXT_LIV_04",
  "HEX_AGR_FOR_03", "HEX_AGR_FOR_04",
  "HEX_AGR_GEN_01",
  "HEX_AGR_FLX_01", "HEX_AGR_FLX_03", "HEX_AGR_FLX_04",
  "HEX_AGR_PAT_01", "HEX_AGR_PAT_04",
  "HEX_CNS_ORG_03", "HEX_CNS_ORG_04",
  "HEX_CNS_DIL_03", "HEX_CNS_DIL_04",
  "HEX_CNS_PER_02",
  "HEX_CNS_PRU_01", "HEX_CNS_PRU_02", "HEX_CNS_PRU_04",
  "HEX_OPN_AES_01", "HEX_OPN_AES_02",
  "HEX_OPN_INQ_03", "HEX_OPN_INQ_04",
  "HEX_OPN_CRE_01", "HEX_OPN_CRE_04",
  "HEX_OPN_UNC_01", "HEX_OPN_UNC_04",
  "HEX_ALT_03", "HEX_ALT_04",
  "NFP_COM_02"
)

d <-
  d_raw %>% 
  rename(
    COL = COL_,
    REL = REL_
    ) %>%
  mutate(
    across(all_of(vars_invert),
    ~ 8 - .x
         ),
    male = case_match(
      GEN,
      c(2, 3) ~ 0,
      1 ~ 1),
    # note that age was coded wrongly; needs to be corrected
    age = case_match(
      AGE,
      1 ~ 1,
      2 ~ 2,
      3 ~ 3,
      4 ~ 4,
      5 ~ 6,
      6 ~ 7,
      7 ~ 5),
    age = set_labels(
      age, 
      labels = c(
        "18-24 years old", 
        "25-34 years old", 
        "35-44 years old", 
        "45-54 years old",
        "55-64 years old", 
        "65+ years old"
      )
    ),
    white = case_match(
      ETH,
      2 ~ 0,
      1 ~ 1),
    relation = case_match(
      REL,
      2 ~ 1,
      1 ~ 0),
    college = case_match(
      COL,
      2 ~ 1,
      1 ~ 0),
    conserv = CON,
    income = INC
  ) 
```

## Labels

We define names and labels for categories of variables, so that we can use them later.

```{r data-labels}
# define vars and labels
vars_ses <- c("age", "male", "white", "relation", "college", "income", "conserv")

vars_ses_txt <- c("Age", "Male", "White", "Relationship", "College", "Income", "Conservatism")

vars_pers_fac <- c("HEX_HOH_SIN", "HEX_HOH_FAI", "HEX_HOH_GRE", "HEX_HOH_MOD",
                   "HEX_ALT",
                   "HEX_EMO_FEA", "HEX_EMO_ANX", "HEX_EMO_DEP", "HEX_EMO_SEN", 
                   "HEX_EXT_SSE", "HEX_EXT_BOL", "HEX_EXT_SOC", "HEX_EXT_LIV", 
                   "HEX_AGR_FOR", "HEX_AGR_GEN", "HEX_AGR_FLX", "HEX_AGR_PAT", 
                   "HEX_CNS_ORG", "HEX_CNS_DIL", "HEX_CNS_PER", "HEX_CNS_PRU", 
                   "HEX_OPN_AES", "HEX_OPN_INQ", "HEX_OPN_CRE", "HEX_OPN_UNC")

vars_pers_fac_txt <- c("Sincerity", "Fairness", "Greed avoidance", "Modesty", 
                       "Altruism",
                       "Fearfulness", "Anxiety", "Dependence", "Sentimentality", 
                       "Social self-esteem", "Social boldness", "Sociability", "Liveliness",
                       "Forgiveness", "Gentleness", "Flexibility", "Patience", 
                       "Organization", "Diligence", "Perfectionism", "Prudence", 
                       "Aesth. appreciation", "Inquisitiveness", "Creativeness", "Unconventionality")

vars_pers_hoh <- 
  c("HEX_HOH", "HEX_HOH_SIN", "HEX_HOH_FAI", "HEX_HOH_GRE", "HEX_HOH_MOD", "HEX_ALT")

vars_pers_emo <- 
  c("HEX_EMO", "HEX_EMO_FEA", "HEX_EMO_ANX", "HEX_EMO_DEP", "HEX_EMO_SEN")

vars_pers_ext <- 
  c("HEX_EXT", "HEX_EXT_SSE", "HEX_EXT_BOL", "HEX_EXT_SOC", "HEX_EXT_LIV")

vars_pers_agr <- 
  c("HEX_AGR", "HEX_AGR_FOR", "HEX_AGR_GEN", "HEX_AGR_FLX", "HEX_AGR_PAT")

vars_pers_cns <- 
  c("HEX_CNS", "HEX_CNS_ORG", "HEX_CNS_DIL", "HEX_CNS_PER", "HEX_CNS_PRU")

vars_pers_opn <- 
  c("HEX_OPN", "HEX_OPN_AES", "HEX_OPN_INQ", "HEX_OPN_CRE", "HEX_OPN_UNC")

vars_pers_all <- 
  c(
    vars_pers_hoh, 
    vars_pers_emo, 
    vars_pers_ext, 
    vars_pers_agr, 
    vars_pers_cns,
    vars_pers_opn
    )

vars_pers_all_txt <- 
  c("Honesty humility", 
      "Sincerity", "Fairness", "Greed avoidance", "Modesty", "Altruism",
    "Emotionality", 
      "Fearfulness", "Anxiety", "Dependence", "Sentimentality", 
    "Extraversion",
      "Social self-esteem", "Social boldness", "Sociability", "Liveliness",
    "Agreeableness",
      "Forgiveness", "Gentleness", "Flexibility", "Patience",
    "Conscientiousness",
      "Organization", "Diligence", "Perfectionism", "Prudence", 
    "Openness",
      "Aesth. appreciation", "Inquisitiveness", "Creativeness", "Unconventionality"
    )

vars_pred_all_txt <- 
  c(
    vars_pers_all_txt,
    vars_ses_txt
    )

vars_pers_dim <- c("HEX_HOH", "HEX_EMO", "HEX_EXT", "HEX_AGR", "HEX_CNS", "HEX_OPN")

vars_pers_dim_txt <- c("Honesty humility", "Emotionality", "Extraversion", 
                       "Agreeableness", "Conscientiousness", "Openness")

vars_pri <- c("NFP_PSY", "NFP_SOC", "NFP_PHY", 
              "NFP_GOV", "NFP_COM", 
              "NFP_INF", "NFP_ANO", "NFP_GEN")

vars_pri_txt <- c("Psychological", "Social", "Physical", 
                  "Government", "Companies", 
                  "Informational", "Anonymity", "General")

vars_pri_txt_brk <- c("Psycho-\nlogical", "Social", "Physical", 
                  "Govern-\nment", "Companies", 
                  "Infor-\nmational", "Anony-\nmity", "General")

vars_pri_txt_abr <- c("Psych.", "Social", "Phys.", 
                  "Gov.", "Comp.", 
                  "Inform.", "Anonym.", "General")

vars_pers_pri <- c(vars_pers_fac, vars_pri)

vars_all <- c(
  vars_pers_all, 
  vars_pri,
  vars_ses
)
```

## Means

Below we compute the means for scales and items.

```{r}
# Person means per facet
d %<>%
  mutate(
    HEX_HOH_M = rowMeans(select(., starts_with("HEX_HOH"))),
    HEX_EMO_M = rowMeans(select(., starts_with("HEX_EMO"))),
    HEX_EXT_M = rowMeans(select(., starts_with("HEX_EXT"))),
    HEX_AGR_M = rowMeans(select(., starts_with("HEX_AGR"))),
    HEX_CNS_M = rowMeans(select(., starts_with("HEX_CNS"))),
    HEX_OPN_M = rowMeans(select(., starts_with("HEX_OPN"))),
    HEX_ALT_M = rowMeans(select(., starts_with("HEX_ALT_0"))),
    HEX_AGR_FLX_M = rowMeans(select(., starts_with("HEX_AGR_FLX_0"))),
    HEX_AGR_FOR_M = rowMeans(select(., starts_with("HEX_AGR_FOR_0"))),
    HEX_AGR_GEN_M = rowMeans(select(., starts_with("HEX_AGR_GEN_0"))),
    HEX_AGR_PAT_M = rowMeans(select(., starts_with("HEX_AGR_PAT_0"))),
    HEX_CNS_DIL_M = rowMeans(select(., starts_with("HEX_CNS_DIL_0"))),
    HEX_CNS_ORG_M = rowMeans(select(., starts_with("HEX_CNS_ORG_0"))),
    HEX_CNS_PER_M = rowMeans(select(., starts_with("HEX_CNS_PER_0"))),
    HEX_CNS_PRU_M = rowMeans(select(., starts_with("HEX_CNS_PRU_0"))),
    HEX_EMO_ANX_M = rowMeans(select(., starts_with("HEX_EMO_ANX_0"))),
    HEX_EMO_DEP_M = rowMeans(select(., starts_with("HEX_EMO_DEP_0"))),
    HEX_EMO_FEA_M = rowMeans(select(., starts_with("HEX_EMO_FEA_0"))),
    HEX_EMO_SEN_M = rowMeans(select(., starts_with("HEX_EMO_SEN_0"))),
    HEX_EXT_BOL_M = rowMeans(select(., starts_with("HEX_EXT_BOL_0"))),
    HEX_EXT_LIV_M = rowMeans(select(., starts_with("HEX_EXT_LIV_0"))),
    HEX_EXT_SOC_M = rowMeans(select(., starts_with("HEX_EXT_SOC_0"))),
    HEX_EXT_SSE_M = rowMeans(select(., starts_with("HEX_EXT_SSE_0"))),
    HEX_HOH_FAI_M = rowMeans(select(., starts_with("HEX_HOH_FAI_0"))),
    HEX_HOH_GRE_M = rowMeans(select(., starts_with("HEX_HOH_GRE_0"))),
    HEX_HOH_MOD_M = rowMeans(select(., starts_with("HEX_HOH_MOD_0"))),
    HEX_HOH_SIN_M = rowMeans(select(., starts_with("HEX_HOH_SIN_0"))),
    HEX_OPN_AES_M = rowMeans(select(., starts_with("HEX_OPN_AES_0"))),
    HEX_OPN_CRE_M = rowMeans(select(., starts_with("HEX_OPN_CRE_0"))),
    HEX_OPN_INQ_M = rowMeans(select(., starts_with("HEX_OPN_INQ_0"))),
    HEX_OPN_UNC_M = rowMeans(select(., starts_with("HEX_OPN_UNC_0"))),
    NFP_ANO_M = rowMeans(select(., starts_with("NFP_ANO_0"))),
    NFP_COM_M = rowMeans(select(., starts_with("NFP_COM_0"))),
    NFP_GEN_M = rowMeans(select(., starts_with("NFP_GEN_0"))),
    NFP_GOV_M = rowMeans(select(., starts_with("NFP_GOV_0"))),
    NFP_INF_M = rowMeans(select(., starts_with("NFP_INF_0"))),
    NFP_PHY_M = rowMeans(select(., starts_with("NFP_PHY_0"))),
    NFP_PSY_M = rowMeans(select(., starts_with("NFP_PSY_0"))),
    NFP_SOC_M = rowMeans(select(., starts_with("NFP_SOC_0")))
  )

# item means
c_m <- 
  c(
    HEX_ALT_m     = mean(d$HEX_ALT_M, na.rm = T),
    HEX_AGR_FLX_m = mean(d$HEX_AGR_FLX_M, na.rm = T),
    HEX_AGR_FOR_m = mean(d$HEX_AGR_FOR_M, na.rm = T),
    HEX_AGR_GEN_m = mean(d$HEX_AGR_GEN_M, na.rm = T),
    HEX_AGR_PAT_m = mean(d$HEX_AGR_PAT_M, na.rm = T),
    HEX_CNS_DIL_m = mean(d$HEX_CNS_DIL_M, na.rm = T),
    HEX_CNS_ORG_m = mean(d$HEX_CNS_ORG_M, na.rm = T),
    HEX_CNS_PER_m = mean(d$HEX_CNS_PER_M, na.rm = T),
    HEX_CNS_PRU_m = mean(d$HEX_CNS_PRU_M, na.rm = T),
    HEX_EMO_ANX_m = mean(d$HEX_EMO_ANX_M, na.rm = T),
    HEX_EMO_DEP_m = mean(d$HEX_EMO_DEP_M, na.rm = T),
    HEX_EMO_FEA_m = mean(d$HEX_EMO_FEA_M, na.rm = T),
    HEX_EMO_SEN_m = mean(d$HEX_EMO_SEN_M, na.rm = T),
    HEX_EXT_BOL_m = mean(d$HEX_EXT_BOL_M, na.rm = T),
    HEX_EXT_LIV_m = mean(d$HEX_EXT_LIV_M, na.rm = T),
    HEX_EXT_SOC_m = mean(d$HEX_EXT_SOC_M, na.rm = T),
    HEX_EXT_SSE_m = mean(d$HEX_EXT_SSE_M, na.rm = T),
    HEX_HOH_FAI_m = mean(d$HEX_HOH_FAI_M, na.rm = T),
    HEX_HOH_GRE_m = mean(d$HEX_HOH_GRE_M, na.rm = T),
    HEX_HOH_MOD_m = mean(d$HEX_HOH_MOD_M, na.rm = T),
    HEX_HOH_SIN_m = mean(d$HEX_HOH_SIN_M, na.rm = T),
    HEX_OPN_AES_m = mean(d$HEX_OPN_AES_M, na.rm = T),
    HEX_OPN_CRE_m = mean(d$HEX_OPN_CRE_M, na.rm = T),
    HEX_OPN_INQ_m = mean(d$HEX_OPN_INQ_M, na.rm = T),
    HEX_OPN_UNC_m = mean(d$HEX_OPN_UNC_M, na.rm = T),
    NFP_ANO_m     = mean(d$NFP_ANO_M, na.rm = T),
    NFP_COM_m     = mean(d$NFP_COM_M, na.rm = T),
    NFP_GEN_m     = mean(d$NFP_GEN_M, na.rm = T),
    NFP_GOV_m     = mean(d$NFP_GOV_M, na.rm = T),
    NFP_INF_m     = mean(d$NFP_INF_M, na.rm = T),
    NFP_PHY_m     = mean(d$NFP_PHY_M, na.rm = T),
    NFP_PSY_m     = mean(d$NFP_PSY_M, na.rm = T),
    NFP_SOC_m     = mean(d$NFP_SOC_M, na.rm = T),
    HEX_HOH_m     = mean(d$HEX_HOH_M, na.rm = T),
    HEX_EMO_m     = mean(d$HEX_EMO_M, na.rm = T),
    HEX_EXT_m     = mean(d$HEX_EXT_M, na.rm = T),
    HEX_AGR_m     = mean(d$HEX_AGR_M, na.rm = T),
    HEX_CNS_m     = mean(d$HEX_CNS_M, na.rm = T),
    HEX_OPN_m     = mean(d$HEX_OPN_M, na.rm = T)
  )

# item standard deviation
c_sd <- 
  c(
    HEX_ALT_sd     = sd(d$HEX_ALT_M, na.rm = T),
    HEX_AGR_FLX_sd = sd(d$HEX_AGR_FLX_M, na.rm = T),
    HEX_AGR_FOR_sd = sd(d$HEX_AGR_FOR_M, na.rm = T),
    HEX_AGR_GEN_sd = sd(d$HEX_AGR_GEN_M, na.rm = T),
    HEX_AGR_PAT_sd = sd(d$HEX_AGR_PAT_M, na.rm = T),
    HEX_CNS_DIL_sd = sd(d$HEX_CNS_DIL_M, na.rm = T),
    HEX_CNS_ORG_sd = sd(d$HEX_CNS_ORG_M, na.rm = T),
    HEX_CNS_PER_sd = sd(d$HEX_CNS_PER_M, na.rm = T),
    HEX_CNS_PRU_sd = sd(d$HEX_CNS_PRU_M, na.rm = T),
    HEX_EMO_ANX_sd = sd(d$HEX_EMO_ANX_M, na.rm = T),
    HEX_EMO_DEP_sd = sd(d$HEX_EMO_DEP_M, na.rm = T),
    HEX_EMO_FEA_sd = sd(d$HEX_EMO_FEA_M, na.rm = T),
    HEX_EMO_SEN_sd = sd(d$HEX_EMO_SEN_M, na.rm = T),
    HEX_EXT_BOL_sd = sd(d$HEX_EXT_BOL_M, na.rm = T),
    HEX_EXT_LIV_sd = sd(d$HEX_EXT_LIV_M, na.rm = T),
    HEX_EXT_SOC_sd = sd(d$HEX_EXT_SOC_M, na.rm = T),
    HEX_EXT_SSE_sd = sd(d$HEX_EXT_SSE_M, na.rm = T),
    HEX_HOH_FAI_sd = sd(d$HEX_HOH_FAI_M, na.rm = T),
    HEX_HOH_GRE_sd = sd(d$HEX_HOH_GRE_M, na.rm = T),
    HEX_HOH_MOD_sd = sd(d$HEX_HOH_MOD_M, na.rm = T),
    HEX_HOH_SIN_sd = sd(d$HEX_HOH_SIN_M, na.rm = T),
    HEX_OPN_AES_sd = sd(d$HEX_OPN_AES_M, na.rm = T),
    HEX_OPN_CRE_sd = sd(d$HEX_OPN_CRE_M, na.rm = T),
    HEX_OPN_INQ_sd = sd(d$HEX_OPN_INQ_M, na.rm = T),
    HEX_OPN_UNC_sd = sd(d$HEX_OPN_UNC_M, na.rm = T),
    NFP_ANO_sd     = sd(d$NFP_ANO_M, na.rm = T),
    NFP_COM_sd     = sd(d$NFP_COM_M, na.rm = T),
    NFP_GEN_sd     = sd(d$NFP_GEN_M, na.rm = T),
    NFP_GOV_sd     = sd(d$NFP_GOV_M, na.rm = T),
    NFP_INF_sd     = sd(d$NFP_INF_M, na.rm = T),
    NFP_PHY_sd     = sd(d$NFP_PHY_M, na.rm = T),
    NFP_PSY_sd     = sd(d$NFP_PSY_M, na.rm = T),
    NFP_SOC_sd     = sd(d$NFP_SOC_M, na.rm = T),
    HEX_HOH_sd     = sd(d$HEX_HOH_M, na.rm = T),
    HEX_EMO_sd     = sd(d$HEX_EMO_M, na.rm = T),
    HEX_EXT_sd     = sd(d$HEX_EXT_M, na.rm = T),
    HEX_AGR_sd     = sd(d$HEX_AGR_M, na.rm = T),
    HEX_CNS_sd     = sd(d$HEX_CNS_M, na.rm = T),
    HEX_OPN_sd     = sd(d$HEX_OPN_M, na.rm = T)
  )
```

# Quality checks
## Missing data

First we filter those who didn't finish the questionnaire.

```{r}
d %<>%
  filter(
    Progress == 100
  )

n_finished <- nrow(d)
```

Let's first inspect missing data.

How many missing do we have?

```{r}
missing_n <- 
  d %>% 
  select(HEX_HOH_SIN_01:CON) %>% 
  n_miss()

missing_per <- 
  d %>% 
  select(HEX_HOH_SIN_01:CON) %>%
  prop_miss() %>% 
  as.numeric() * 100
```

Only `r missing_n` cells are missing -- which is very little. To be precise, `r missing_per %>% round(4)` percent only. 

Which variables are affected?

```{r}
d %>% 
  select(HEX_HOH_SIN_01:CON) %>% 
  miss_var_summary() %>% 
  head(19)
```

Missing answers vary randomly across variables.

How about participants?

```{r}
d %>% 
  select(HEX_HOH_SIN_01:CON) %>% 
  miss_case_summary()
```

Only six participants with missing data, and even then, not much. We hence decided to keep everyone.

## Speeders

We preregistered to remove participants faster than 3 standard deviations than the median response time.

```{r cache=F}
# Median response time
time_med <- median(d$Duration__in_seconds_)

# Average response time
time_m <- mean(d$Duration__in_seconds_) / 60

# Standard deviation
time_sd <- sd(d$Duration__in_seconds_)

# filter speeders
time_crit_init <- time_med - (3 * time_sd) # minimum time on survey
```

However, this made little sense. The median response time was `r time_med` seconds and the standard deviation `r time_sd %>% round(0)` seconds. Hence, three SDs below median was `r time_crit_init %>% round(0)` seconds, hence not informative. 

Instead, we decided to remove respondents who took less than five minutes answering the questionnaire, which we considered unreasonably fast.

```{r cache=F}
time_crit <- 5 * 60

# count number of speeders
n_speeding <- 
  nrow(
    filter(
      d, 
      Duration__in_seconds_ < time_crit
      )
    )

# Deletion of fast respondents
d <- 
  filter(
    d, 
    Duration__in_seconds_ >= time_crit
    )

n_used <- nrow(d)
```

Average response time was `r time_m %>% round(0)` minutes. We removed `r n_speeding` because they answered the survey unreasonably fast.

## Response patterns

Let's inspect for potential response patterns. We'll do so looking at influential cases, which we'll then inspect manually.

We'll use raw data, so that inverted items aren't recoded and patterns become more visible. (Note that this data set isn't yet filtered for speeders).

```{r}
options(mc.cores = 8)

# analyses require complete cases only
d_raw_compl <- d_raw %>% 
  select(ID, Duration__in_seconds_, HEX_HOH_SIN_01:PRI_BEH) %>% 
  .[complete.cases(.), ]

outliers <- 
  check_outliers(
    d_raw_compl, 
    method = "all", 
    verbose = FALSE
  )

summary(outliers)
```

194 outliers were detected. We'll now inspect these outliers manually.

```{r}
d_outliers_stats <- as.data.frame(outliers)

d_outliers <- 
  d_raw_compl[d_outliers_stats$Outlier >= 0.5, ] %>%
  as.data.frame()

d_outliers

patterns <- c(
  449      # "R_72Kshi80pwPq9Gy"
  , 6      # "R_5OrhZQwvj9wfJWp"
  , 705    # "R_5QSPlArm0BtfIrE"
  , 1422   # "R_3Cv1Tmj5HX4ghJU"
  , 1401   # "R_5Pld7hbh1ay8sb7"
  , 1355   # "R_4DuqyujkQ7Hjapj"
  , 273    # "R_6MqzefRkB3aQdPj"
  , 747    # "R_7QSq0FbgZfcnJIt"
  , 1406   # "R_1MrHTg5CZpBLeYw"
  )
```


The following `r length(patterns) %>% english::english()` cases show clear patterns and will be removed.

```{r}
d_filtered <- filter(d, ID %in% patterns)
d_filtered

d <- filter(d, !ID %in% patterns)
n_final <- nrow(d)
```

# Save Workspace

```{r cache=F}
save.image("data/workspace_2.RData")
```
