---
title: "Readability analyses of items"
output:
  html_document:
    toc: TRUE
    toc_float:
      collapsed: FALSE
    toc_depth: 2
    code_folding: hide
bibliography      : 
  - "bibliography/r-references.bib"
  - "bibliography/references.bib"
  # pdf_document:
  #   toc: TRUE
---

```{r knitr-setup, include=F}
set.seed(170819)
knitr::opts_chunk$set(warning=F, echo=F, error=F, message=F, cache = T, 
                      tidy=T, dev = 'pdf', cache.extra = knitr::rand_seed)
options(digits = 3, width = 90)
```

```{r r-setup, include=F}
# install packages
# devtools::install_github("https://github.com/tdienlin/td")

# define packages
packages <- c("corrplot", "devtools", "GGally", "ggplot2", "haven", "kableExtra", "knitr", 
              "lavaan", "magrittr", "mice", "MVN", "PerFit", "psych", "quanteda.textstats",
              "pwr", "semPlot", "semTools", "tidyverse", "td")

# load packages
lapply(packages, library, character.only = TRUE)

# readability function
readability = function(data){
  reading_estimates <- c("Flesch.Kincaid", "FOG", "Coleman.Liau.short", "Dale.Chall.PSK")
  textstat_readability(data, measure = reading_estimates) %>% 
    as.data.frame %>% 
    mutate(average = rowMeans(select(., -document)))
}
```

```{r data-wrangling}
d <- read_spss("data/Need+for+Privacy_August+16%2C+2021_15.33.sav")
```

Below, we develop several new items for need for privacy. To validate items, we follow the procedure implemented by @patalayAssessingReadabilitySelfreported2018 and calculate the following four reading scores: Flesch–Kincaid reading grade (FK), Gunning Fog Index (GFI), Coleman Liau Index (CLI), and the Powers-Sumner-Kearl Variation of the Dale and Chall Readability formula (DC).

# Personality

To have a benchmark, we calculated the readability of the HEXACO items. It was as follows:

```{r}
items_hexaco <- c(
  "If I want something from a person I dislike, I will act very nicely toward that person in order to get it.", 
 "I wouldn't use flattery to get a raise or promotion at work, even if I thought it would succeed.", 
 "If I want something from someone, I will laugh at that person's worst jokes.", 
 "I wouldn't pretend to like someone just to get that person to do favors for me.", 
 "If I knew that I could never get caught, I would be willing to steal a million dollars.", 
 "I would be tempted to buy stolen property if I were financially tight.", 
 "I would never accept a bribe, even if it were very large.", 
 "I’d be tempted to use counterfeit money, if I were sure I could get away with it.", 
 "Having a lot of money is not especially important to me.", 
 "I would like to live in a very expensive, high-class neighborhood.", 
 "I would like to be seen driving around in a very expensive car.", 
 "I would get a lot of pleasure from owning expensive luxury goods.", 
 "I am an ordinary person who is no better than others.", 
 "I wouldn’t want people to treat me as though I were superior to them.", 
 "I think that I am entitled to more respect than the average person is.", 
 "I want people to know that I am an important person of high status.", 
 "I would feel afraid if I had to travel in bad weather conditions.", 
 "I don’t mind doing jobs that involve dangerous work.", 
 "When it comes to physical danger, I am very fearful.", 
 "Even in an emergency I wouldn't feel like panicking.", 
 "I sometimes can't help worrying about little things.", 
 "I worry a lot less than most people do.", 
 "I rarely, if ever, have trouble sleeping due to stress or anxiety.", 
 "I get very anxious when waiting to hear about an important decision.", 
 "When I suffer from a painful experience, I need someone to make me feel comfortable.", 
 "I can handle difficult situations without needing emotional support from anyone else.", 
 "Whenever I feel worried about something, I want to share my concern with another person.", 
 "I rarely discuss my problems with other people.", 
 "I feel like crying when I see other people crying.", 
 "When someone I know well is unhappy, I can almost feel that person's pain myself.", 
 "I feel strong emotions when someone close to me is going away for a long time.", 
 "I remain unemotional even in situations where most people get very sentimental.", 
 "I feel reasonably satisfied with myself overall.", 
 "I think that most people like some aspects of my personality.", 
 "I feel that I am an unpopular person.", 
 "Even in an emergency I wouldn't feel like panicking.", 
 "I rarely express my opinions in group meetings.", 
 "In social situations, I'm usually the one who makes the first move.", 
 "When I'm in a group of people, I'm often the one who speaks on behalf of the group.", 
 "I tend to feel quite self-conscious when speaking in front of a group of people.", 
 "I avoid making 'small talk' with people.", 
 "I enjoy having lots of people around to talk with.", 
 "I prefer jobs that involve active social interaction to those that involve working alone.", 
 "The first thing that I always do in a new place is to make friends.", 
 "I am energetic nearly all the time.", 
 "On most days, I feel cheerful and optimistic.", 
 "People often tell me that I should try to cheer up.", 
 "Most people are more upbeat and dynamic than I generally am.", 
 "I rarely hold a grudge, even against people who have badly wronged me.", 
 "My attitude toward people who have treated me badly is 'forgive and forget'.", 
 "If someone has cheated me once, I will always feel suspicious of that person.", 
 "I find it hard to fully forgive someone who has done something mean to me.", 
 "People sometimes tell me that I am too critical of others.", 
 "I generally accept people’s faults without complaining about them.", 
 "I tend to be lenient in judging other people.", 
 "Even when people make a lot of mistakes, I rarely say anything negative.", 
 "People sometimes tell me that I'm too stubborn.", 
 "I am usually quite flexible in my opinions when people disagree with me.", 
 "When people tell me that I’m wrong, my first reaction is to argue with them.", 
 "I find it hard to compromise with people when I really think I’m right.", 
 "People think of me as someone who has a quick temper.", 
 "I rarely feel anger, even when people treat me quite badly.", 
 "Most people tend to get angry more quickly than I do.", 
 "I find it hard to keep my temper when people insult me.", 
 "I clean my office or home quite frequently.", 
 "I plan ahead and organize things, to avoid scrambling at the last minute.", 
 "People often joke with me about the messiness of my room or desk.", 
 "When working, I sometimes have difficulties due to being disorganized.", 
 "When working, I often set ambitious goals for myself.", 
 "I often push myself very hard when trying to achieve a goal.", 
 "Often when I set a goal, I end up quitting without having reached it.", 
 "I do only the minimum amount of work needed to get by.", 
 "I often check my work over repeatedly to find any mistakes.", 
 "When working on something, I don't pay much attention to small details.", 
 "I always try to be accurate in my work, even at the expense of time.", 
 "People often call me a perfectionist.", 
 "I make decisions based on the feeling of the moment rather than on careful thought.", 
 "I make a lot of mistakes because I don't think before I act.", 
 "I don’t allow my impulses to govern my behavior.", 
 "I prefer to do whatever comes to mind, rather than stick to a plan.", 
 "I would be quite bored by a visit to an art gallery.", 
 "I wouldn't spend my time reading a book of poetry.", 
 "If I had the opportunity, I would like to attend a classical music concert.", 
 "Sometimes I like to just watch the wind as it blows through the trees.", 
 "I'm interested in learning about the history and politics of other countries.", 
 "I enjoy looking at maps of different places.", 
 "I would be very bored by a book about the history of science and technology.", 
 "I’ve never really enjoyed looking through an encyclopedia.", 
 "I would like a job that requires following a routine rather than being creative.", 
 "I would enjoy creating a work of art, such as a novel, a song, or a painting.", 
 "People have often told me that I have a good imagination.", 
 "I don't think of myself as the artistic or creative type.", 
 "I think that paying attention to radical ideas is a waste of time.", 
 "I like people who have unconventional views.", 
 "I think of myself as a somewhat eccentric person.", 
 "I find it boring to discuss philosophy.", 
 "I have sympathy for people who are less fortunate than I am.", 
 "I try to give generously to those in need.", 
 "It wouldn’t bother me to harm someone I didn’t like.", 
 "People see me as a hard-hearted person."
)
readability_hexaco <- readability(items_hexaco)
readability_hexaco <- colMeans(select(readability_hexaco, -document))
readability_hexaco <- data.frame(document = "HEXACO", as.list(readability_hexaco))
readability_hexaco
```

Readability was good. The results means that, on average, understanding the items requires seven years of schooling.

# Privacy
## Horizontal
### Psychological

@frenerDevelopmentValidationNeed2021

 1.	I don’t like to talk about personal issues with others unless they do it first.
 2.	There are a lot of things about me that I don’t like to talk about with others.
 3.	I prefer not to share my feelings and inner thoughts with others.
 4.	I do not like it when others talk to me about their private issues. (new)

```{r}
items <- c(
 "I don’t like to talk about personal issues with others unless they do it first.",
 "There are a lot of things about me that I don’t like to talk about with others.",
 "I prefer not to share my feelings and inner thoughts with others.",
 "I do not like it when others talk to me about their private issues."
)
readability(items) %>% rbind(readability_hexaco)
```

Readability looks good!

### Physical

@frenerDevelopmentValidationNeed2021

 1.	I don’t like it when strangers come too close to me.
 2.	I don’t like to stand in a dense crowd of people.
 3.	I don’t like to sit next to a stranger on a tram, bus, or plane.
 4.	I hate it when people enter my personal space uninvited. (new)

```{r}
items <- c(
 "I don’t like it when strangers come too close to me.",
 "I don’t like to stand in a dense crowd of people.",
 "I don’t like to sit next to a stranger on a tram, bus, or plane.",
 "I hate it when people enter my personal space uninvited."
)
readability(items) %>% rbind(readability_hexaco)
```

Looks good. (Item 4 not perfect, but it should still work.)

### Social Privacy

@dienlinWhoNeedsPrivacy2019

 1.	I don’t feel comfortable interacting with other people. [@harrisonDevelopmentDesirePrivacy1993]
 2.	I often want to be alone. (new)
 3.	I’m a fairly anti-social person. (new)
 4.	I prefer to work independently in most situations. (new)
 
```{r}
items <- c(
 "My need for privacy is so strong that it prevents me from using social media actively.",
 "I don’t feel I need to tell my friends all my secrets.",
 "I feel I need to protect my privacy from other people.",
 "I prefer it when others don’t know much about me."
)
readability(items) %>% rbind(readability_hexaco)
```

Readability looks good. (Item 1 not perfect, but should still work and was already validated.)

## Vertical
### Privacy from Government

@dienlinWhoNeedsPrivacy2019

 - I need government agencies to respect my privacy, even if that hinders a greater societal cause, such as catching criminals.
 - I don’t want the government to gather information about me, even if that makes it more difficult for them to spend tax income efficiently.
 - I don’t want government agencies to monitor my personal communication, even if doing so prevents future terrorist attacks.
 - I feel I need to protect my privacy from government agencies. 

```{r}
items_old <- c(
 "I need government agencies to respect my privacy, even if that hinders a greater societal cause, such as catching criminals.",
 "I don’t want the government to gather information about me, even if that makes it more difficult for them to spend tax income efficiently.",
 "I don’t want government agencies to monitor my personal communication, even if doing so prevents future terrorist attacks.",
 "I feel I need to protect my privacy from government agencies."
)
readability(items_old) %>% rbind(readability_hexaco)
```

Items 1, 2 and 3 show rather high scores. Try to formulate easier.

New items:

 1.	I need government agencies to respect my privacy, even if that makes catching criminals harder.
 2.	I don’t want the government to gather data about me, even if that makes it harder to spend tax income effectively.
 3.	I don’t want government agencies to monitor my communication, even if that stops terrorist attacks.
 4.	I feel I need to protect my privacy from government agencies.
  
```{r}
items_new <- c(
 "I need government agencies to respect my privacy, even if that makes catching criminals harder.",
 "I don’t want the government to gather data about me, even if that makes it harder to spend tax income effectively.",
 "I don’t want government agencies to monitor my communication, even if that stops terrorist attacks.",
 "I feel I need to protect my privacy from government agencies."
)
readability(items_new) %>% rbind(readability_hexaco)
```

A bit better, but not much. But scale worked pretty well in original study, so should be okay.

```{r}
model <- "NFP_INT =~ NFP_INT_01 + NFP_INT_02 + NFP_INT_03 + NFP_INT_04"
```

### Privacy from Companies

New, self-designed.

 1. I’m willing to pay more for products or services so that companies don’t have to sell my data.
 2. I’m happy to give up a little bit of privacy, so that I can use certain apps or services for free.
 3. I don’t want companies to gather information about me, even if that reduces the quality of their services.
 4. I feel I need to protect my privacy from companies.

```{r}
items <- c(
 "I’m willing to pay more for products or services so that companies don’t have to sell my data.",
 "I’m happy to give up a little bit of privacy, so that I can use certain apps or services for free.",
 "I don’t want companies to gather information about me, even if that reduces the quality of their services.",
 "I feel I need to protect my privacy from companies."
)
readability(items) %>% rbind(readability_hexaco)
```

Items 3 seems to be a bit too difficult. Try to make easier.

 1. I’m willing to pay more for products or services so that companies don’t have to sell my data.
 2. I’m happy to give up a little bit of privacy so that I can use certain apps or services for free.
 3. I don’t want companies to collect data about me, even if that makes their services worse.
 4. I feel I need to protect my privacy from companies.
	
```{r}
items <- c(
	"I’m willing to pay more for products or services so that companies don’t have to sell my data.",
	"I’m happy to give up a little bit of privacy so that I can use certain apps or services for free.",
	"I don’t want companies to collect data about me, even if that makes their services worse.",
	"I feel I need to protect my privacy from companies."
)
readability(items) %>% rbind(readability_hexaco)
```

Readability now much better.

## General
### Informational

@frenerDevelopmentValidationNeed2021

 1.	I would prefer that little is known about me.
 2.	I don’t want my personal data to be publicly accessible.
 3.	It is important to me that records pertaining to me remain confidential. [@harrisonDevelopmentDesirePrivacy1993]
 4.	I prefer that others cannot easily find information about me on the Internet. (new)
 
```{r}
items <- c(
	"I would prefer that little is known about me.",
 	"I don’t want my personal data to be publicly accessible.",
 	"It is important to me that records pertaining to me remain confidential.",
  "I prefer that others cannot easily find information about me on the Internet."
)
readability(items) %>% rbind(readability_hexaco)
```

Readability looks good.

### Privacy need anonymity

@dienlinWhoNeedsPrivacy2019

 1.	I would prefer to use a fake account on social network sites to preserve my privacy.
 2.	I feel I need to avoid places with video surveillance.
 3.	I prefer not to carry my driver’s license or ID with me all the time to preserve my privacy.
 4.	I need to be able to surf the Internet anonymously. (new)
 
```{r}
items <- c(
 "I would prefer to use a fake account on social network sites to preserve my privacy.",
 "I feel I need to avoid places with video surveillance.",
 "I prefer not to carry my drivers license or ID with me all the time to preserve my privacy.",
 "I need to be able to surf the Internet anonymously."
)
readability(items) %>% rbind(readability_hexaco)
```

Readability looks good.

### General Need for privacy

New, self-designed.

 1.	I need a lot of privacy.
 2.	Privacy is very important to me.
 3.	I think a lot about how I can protect my privacy.
 4.	I value privacy a lot.

```{r}
items <- c(
  "I need a lot of privacy.",
  "Privacy is very important to me.",
  "I think a lot about how I can protect my privacy.",
  "I need a lot of time for myself."
)
readability(items) %>% rbind(readability_hexaco)
```

Readability was good.